Iterative Monomorphisation

### 2024-07-08 iterative_monomorphisation.tex
more

As a precaution against overfitting, we carried out the part of the evaluation related to parameter optimisation and all preliminary evaluations on 500 randomly chosen problems out of the 1534 selected problems. We carried out the rest of the evaluation on the remaining 1034 problems. Before finding values to assign to the bounds of the monomorphisation algorithm, we must make the choice of the base options used to run Zipperposition. Zipperposition has a portfolio mode with several configurations. Because the space of possible base configurations is too large to evaluate, we (informally?) evaluated, in a preliminary experiment, all portfolio configurations that called E against our benchmark suite of 500 problems, without using monomorphisation. The best performing configuration became the base configuration, which we used as a basis to evaluate the different monomorphisation options. Our (informal?) evaluation found that the so-called \verb|40_b.comb| configuration performed best by proving 131 problems. %[TODO discuss with Jasmin]
We conducted additionnal informal preliminary evaluations on the 500 problems benchmark suite to find appropriate default values and test ranges for the monomorphisation bounds. We started the option evaluation process with base configuration \verb|40_b.comb|, with the following default values for the monomorphisation bounds:

>>>>

As a precaution against overfitting, we carried out the part of the evaluation related to parameter optimisation and all preliminary evaluations on 500 randomly chosen problems out of the 1534 selected problems. We carried out the rest of the evaluation on the remaining 1034 problems. Before finding values to assign to the bounds of the monomorphisation algorithm, we must make the choice of the base options used to run Zipperposition. Zipperposition has a portfolio mode with several configurations. Because the space of possible base configurations is too large to evaluate, we evaluated, in a preliminary experiment, all portfolio configurations that called E against our benchmark suite of 500 problems, without using monomorphisation. The best performing configuration became the base configuration, which we used as a basis to evaluate the different monomorphisation options. Our preliminary evaluation found that the so-called \verb|40_b.comb| configuration performed best by proving 131 problems.
We conducted additionnal informal preliminary evaluations on the 500 problems benchmark suite to find appropriate default values and test ranges for the monomorphisation bounds. We started the option evaluation process with base configuration \verb|40_b.comb|, with the following default values for the monomorphisation bounds:
